|

### 2020-07-06 analysis/paper/paper.Rmd
equate sampling occassions to surveys
change integrated pop model to integrated model

for surveys $k=1, ..., K$.
This is the observation model used in N-mixture models [@royle2004n]. 
In addition to potentially providing a higher lower bound on abundance, auxiliary encounters also provide additional information about encounter probabilities, because the encounter data are conditionally independent from encounters leading to captures. 
When combined with the capture-recapture model outlined above, the joint model of captures, failed captures, and auxiliary encounters comprise an integrated population model [@besbeas2002integrating; @abadi2010assessment]. 
The posterior distribution is proportional to:

@@

Conceptual diagram to represent the data model for individuals $i=1, ..., M$ and sampling occasions $k=1, ..., K$. Each individual is either in the population ($z_i=1$) or not ($z_i=0$). Those that are not are never encountered. Those that are may be encountered on occasion $k$ or not, and encountered individuals may or may not be captured and identified (we assume that identification requires capture, so that capture and identification are synonymous). Each path leads to a value of the partly observed quantity $y^*_{i, k}$, where $y^*_{i, k}=1$ when animals are not encountered, $y^*_{i, k}=2$ when animals are encountered but not identified, and $y^*_{i, k}=3$ when animals are encountered and identified.

>>>>

for surveys $k=1, ..., K$.
This is the observation model used in N-mixture models [@royle2004n]. 
In addition to potentially providing a higher lower bound on abundance, auxiliary encounters also provide additional information about encounter probabilities, because the encounter data are conditionally independent from encounters leading to captures. 
When combined with the capture-recapture model outlined above, the joint model of captures, failed captures, and auxiliary encounters comprise an integrated model [@besbeas2002integrating; @abadi2010assessment]. 
The posterior distribution is proportional to:

@@

Conceptual diagram to represent the data model for individuals $i=1, ..., M$ and sampling occasions or surveys $k=1, ..., K$. Each individual is either in the population ($z_i=1$) or not ($z_i=0$). Those that are not are never encountered. Those that are may be encountered on occasion $k$ or not, and encountered individuals may or may not be captured and identified (we assume that identification requires capture, so that capture and identification are synonymous). Each path leads to a value of the partly observed quantity $y^*_{i, k}$, where $y^*_{i, k}=1$ when animals are not encountered, $y^*_{i, k}=2$ when animals are encountered but not identified, and $y^*_{i, k}=3$ when animals are encountered and identified.
